---
title: "Locations and LUH"
author: "JayToh"
date: '2023-05-21'
output: html_document
---

# Library:
```{r}
library(dplyr)
```

# Data:
Dataset from 2.Grouping. There are four datasets, where Animals have two (one from PREDICTS and another siteMetric dataset from Newbold et al. (2020)), Plants one, and fungi one. 
```{r}

Animals <- read.csv("1.AnimalFG.csv") %>% select(-X.1, -X) %>% relocate(Longitude, Latitude)
Plants <- read.csv("2.z`PlantFG.csv") %>% select(-X.1, -X) %>% relocate(Longitude, Latitude)
Fungi <- read.csv("3.FungiFG.csv") %>% select(-X.1, -X) %>% relocate(Longitude, Latitude)

### Location from LUH ###
Lonlat <- read.csv("Lonlat_df.csv") %>% select(-X)
```



# Simplify:
```{r}
############# Function that simplify names #############
Ezsimplify <- function(df) {
  A <- df %>% mutate(Land_use = Predominant_land_use) %>% relocate(Land_use, .after = Predominant_land_use) %>% relocate(Use_intensity, .after = Land_use) %>% mutate(Intensity = Use_intensity) %>% relocate(Intensity, .after = Use_intensity)
  A$Land_use <- dplyr::recode(A$Predominant_land_use,
                                                       "Primary vegetation" = "PV",
                                                       "Young secondary vegetation" = "SV",
                                                       "Intermediate secondary vegetation" = "SV",
                                                       "Mature secondary vegetation" = "SV",
                                                       "Secondary vegetation (indeterminate age)" = "SV",
                                                       "Plantation forest" = "Plantation",
                                                       "Cropland" = "Crop")
  A$Intensity <- dplyr::recode(A$Use_intensity,
                                                       "Minimal use" = "Minimal",
                                                       "Light use" = "Light",
                                                       "Intense use" = "Intense")
  A$SSS <- factor(A$SSS)
  A$Source_ID <- factor(A$Source_ID)
  A$SS <- factor(A$SS)
  A
}

############# Simplified Dataframe here #############
count(AnimalFG, LandUse) # Human-dominated, PV, SV

Animals_simplified <- Ezsimplify(Animals)
Plants_simplified <- Ezsimplify(Plants)  
Fungi_simplified <- Ezsimplify(Fungi) 

rm(Animals, Plants, Fungi)

#### Checking ####
dplyr::count(Animals, Land_use)
```

# Converting locations
## Lon, Lat, Land use
Preparing for matching into gridded cells
1. Column for general land use (Natural vs Artificial)
2. Remove locations with NAs
```{r}
EzNoNa <- function(DF){
  A <- DF
  B <- A %>% mutate(General_land_use = ifelse(Land_use == "PV" |Land_use == "SV", "Natural", "Artificial")) %>% relocate(General_land_use, .after = Land_use)
  C <- B[complete.cases(B[, 1:2]),] # Column 1 and 2 are Lon and Lat respectfully
  C
}

EzNoNa2 <- function(DF){
  A <- DF
  C <- A[complete.cases(A[, 11:12]),] # Column 8 and 9 are Lon and Lat respectfully
  C
}

Animals_lonlat <- EzNoNa(Animals_simplified) # Removed 1,232 records
Plants_lonlat <- EzNoNa(Plants_simplified)
Fungi_lonlat <- EzNoNa(Fungi_simplified)

rm(Animals_simplified, Plants_simplified, Fungi_simplified)
```

## LUH gridded locations 
```{r}
lon_df <- Lonlat %>% select(Lon, Lon_max, Lon_min) %>% mutate(X = 1) %>% group_by(Lon, Lon_max, Lon_min) %>% summarise(Y = sum(X)) %>% select(-Y) # should have 1440. YES!
lat_df <- Lonlat %>% select(Lat, Lat_max, Lat_min) %>% mutate(X = 1) %>% group_by(Lat, Lat_max, Lat_min) %>% summarise(Y = sum(X)) %>% select(-Y) # should have 720. YES!
```

## Gridding 
1. Convert exact locations from PREDICTS to gridded locations used in LUH (Watch out for # of rows, data can duplicate with left_join)
```{r}
########### Function for matching PREDICTS location to gridded cells ###########
Ezforlocation <- function(DF) {
  #### Longitude ####
  A <- DF$Longitude
  B <- numeric() # For storing data later from each iteration
  for(values in 1:length(A)) {
  B[values]  <- ifelse(A[values] < lon_df$Lon_max & A[values] >= lon_df$Lon_min, lon_df$Lon, NA) %>% na.omit() %>% as.numeric()
  }
  
  C <- B %>% data.frame(Lon = A, Lon_grid = B)
  C <- C[,2:3] # The first column is repeated, so no need to keep it. Only the second and third column have the original longitude and grid longitude respectfully
  
  #### Latitude ####
  D <- DF$Latitude
  E <- numeric() # For storing data later from each iteration
  for(values in 1:length(D)) {
  E[values]  <- ifelse(D[values] < lat_df$Lat_max & D[values] >= lat_df$Lat_min, lat_df$Lat, NA) %>% na.omit() %>% as.numeric()
  }
  
  FF <- E %>% data.frame(Lat = D, Lat_grid = E)
  FF <- FF[,2:3]
  G <- cbind(C, FF) %>% relocate(Lat, .after = Lon) # Combine longitude and latitude together into one data frame
  
  Final_DF <- cbind(DF, G) %>% 
    relocate(Lon, .after=  Longitude) %>% 
    relocate(Lat, .after = Latitude) %>% 
    relocate(Lon_grid, .after = Lon) %>% 
    relocate(Lat_grid, .after = Lat)
  Final_DF
}

####### Converted dataset here! #######
# Can take a few minutes to run, be patient!
Animals_Final <- Ezforlocation(Animals_lonlat)
Plants_Final <- Ezforlocation(Plants_lonlat)
Fungi_Final <- Ezforlocation(Fungi_lonlat)

rm(Animals_lonlat, Plants_lonlat, Fungi_lonlat, lat_df, lon_df, Lonlat)  
#------------------------------------------ Raw codes for testing ------------------------------------------#
CC <- numeric()
CL <- c(Consumers1$Longitude)
 for(values in 1:length(CL)) {
  CC[values]  <- ifelse(CL[values] <= lon_df$Lon_max & CL[values] >= lon_df$Lon_min, lon_df$Lon, NA) %>% na.omit() %>% as.numeric()
}
CC
```

# Years_since
```{r}
Natural_conversion <- readRDS("Natural_conversion.rds") %>% select(Lon, Lat, Last_conversion_forward, Since_conversion_forward, Last_conversion_backward, Since_conversion_backward) %>% rename("First_conversion" = "Last_conversion_forward",                                                                                                        "Since_first_conversion" = "Since_conversion_forward", 
                                                                "Last_conversion" = "Last_conversion_backward", 
                                                                "Since_Last_conversion" = "Since_conversion_backward") %>% 
  rename("Lon_grid" = "Lon", "Lat_grid" = "Lat")


### Testing ###
Testing <- readRDS("Natural_conversion.rds")
Testing1 <- rbind(Testing %>% filter(Lon == 46.375, Lat == -24.875),
                  Testing %>% filter(Lon == 21.625, Lat == 50.375),
                  Testing %>% filter(Lon == -32.875, Lat == 83.125),
                  Testing %>% filter(Lon == -77.125, Lat == 43.875))

rm(Testing, Testing1)
```

## Animals match:
```{r}
Animals_converted <- dplyr::left_join(Animals_Final, Natural_conversion, by = c("Lon_grid", "Lat_grid")) %>% relocate(First_conversion, Since_first_conversion, Last_conversion, Since_Last_conversion, .after = Years_since_fragmentation_or_conversion)


dplyr::count(Animals_converted %>% mutate(Is_same = (Years_since_fragmentation_or_conversion == Since_Last_conversion)), Is_same)


```

## Plants match:
```{r}
Plants_converted <- dplyr::left_join(Plants_Final, Natural_conversion, by = c("Lon_grid", "Lat_grid")) %>% relocate(First_conversion, Since_first_conversion, Last_conversion, Since_Last_conversion, .after = Years_since_fragmentation_or_conversion)

dplyr::count(Plants_converted %>% mutate(Is_same = (Years_since_fragmentation_or_conversion == Since_Last_conversion)), Is_same)
```

## Fungi match:
```{r}
Fungi_converted <- dplyr::left_join(Fungi_Final, Natural_conversion, by = c("Lon_grid", "Lat_grid")) %>% relocate(First_conversion, Since_first_conversion, Last_conversion, Since_Last_conversion, .after = Years_since_fragmentation_or_conversion)

dplyr::count(Fungi_converted %>% mutate(Is_same = (Years_since_fragmentation_or_conversion == Since_Last_conversion)), Is_same)
```

# Export data:
Export data for diversity calculation
```{r}
saveRDS(Animals_converted, "Animals_converted.rds")
saveRDS(Plants_converted, "Plants_converted.rds")
saveRDS(Fungi_converted, "Fungi_converted.rds")
```



