---
title: "Effect of Time since Land use conversion"
author: "JayToh"
date: '2023-03-29'
output: html_document
---

# Library:
```{r}
library(dplyr)
library(predictsFunctions)
```

# Data
```{r}
PREDICTS <- read.csv("database.csv")

```

# Cleaning
1. Rescaling sampling effort within each study, where the most-sampled site gets a relative effort value of 1, and the sampling effort for all other sites is scaled linearly relative to the maximum value
2. combine sites with identical coordinates, belonging to the same study and spatial block of sites, sampled on the same dates, sampled with the same methods and recorded using the same diversity metric, and situated within the same land-use type and human land-use intensity
3. Filter out Protozoa (not the scope of this study)
```{r}
PREDICTS_corrected <- predictsFunctions::CorrectSamplingEffort(diversity = PREDICTS) %>% predictsFunctions::MergeSites(silent = TRUE)
PREDICTS_corrected <- PREDICTS_corrected %>% filter(!(Kingdom == "Protozoa"))
```

# Quick check of data
```{r}
PREDICT_summary <- dplyr::count(PREDICTS_corrected, Kingdom) %>% rename("Records" = "n") %>% 
  mutate(Phylum = c(nrow(count(PREDICTS_corrected %>% filter(Kingdom == "Animalia"), Phylum)),
                    nrow(count(PREDICTS_corrected %>% filter(Kingdom == "Plantae"), Phylum)),
                    nrow(count(PREDICTS_corrected %>% filter(Kingdom == "Fungi"), Phylum)))) %>% 
  mutate(Class = c(nrow(count(PREDICTS_corrected %>% filter(Kingdom == "Animalia"), Class)),
                    nrow(count(PREDICTS_corrected %>% filter(Kingdom == "Plantae"), Class)),
                    nrow(count(PREDICTS_corrected %>% filter(Kingdom == "Fungi"), Class)))) %>% 
  mutate(Order = c(nrow(count(PREDICTS_corrected %>% filter(Kingdom == "Animalia"), Order)),
                    nrow(count(PREDICTS_corrected %>% filter(Kingdom == "Plantae"), Order)),
                    nrow(count(PREDICTS_corrected %>% filter(Kingdom == "Fungi"), Order)))) %>% 
  mutate(Richness = c(nrow(PREDICTS_corrected %>% filter(Kingdom == "Animalia" & Diversity_metric == "species richness")),
                      nrow(PREDICTS_corrected %>% filter(Kingdom == "Plantae" & Diversity_metric == "species richness")),
                      nrow(PREDICTS_corrected %>% filter(Kingdom == "Fungi" & Diversity_metric == "species richness")))) %>% 
  mutate(Abundance = c(nrow(PREDICTS_corrected %>% filter(Kingdom == "Animalia" & Diversity_metric == "abundance")),
                      nrow(PREDICTS_corrected %>% filter(Kingdom == "Plantae" & Diversity_metric == "abundance")),
                      nrow(PREDICTS_corrected %>% filter(Kingdom == "Fungi" & Diversity_metric == "abundance")))) %>% 
  mutate(Occurrence = c(nrow(PREDICTS_corrected %>% filter(Kingdom == "Animalia" & Diversity_metric == "occurrence")),
                      nrow(PREDICTS_corrected %>% filter(Kingdom == "Plantae" & Diversity_metric == "occurrence")),
                      nrow(PREDICTS_corrected %>% filter(Kingdom == "Fungi" & Diversity_metric == "occurrence"))))
                     

# Animalia	1441328			
# Fungi	    97470			
# Plantae	  1368089


count(PREDICTS_corrected, Diversity_metric)
```

# Exporting data:
Data exported based on the kingdoms
```{r}
Animal <- PREDICTS_corrected %>% filter(Kingdom == "Animalia")
Plant <- PREDICTS_corrected %>% filter(Kingdom == "Plantae")
Fungi <- PREDICTS_corrected %>% filter(Kingdom == "Fungi")

write.csv(PREDICTS_corrected, "PREDICTS_cleaned.csv")

write.csv(Plant, "Plant.csv")
write.csv(Animal, "Animal.csv")
write.csv(Fungi, "Fungi.csv")


```

# Animals diversity
```{r}
sites <- predictsFunctions::SiteMetrics(diversity = PREDICTS_corrected,
                                           extra.cols = c("Longitude","Latitude",
                                                          "Predominant_land_use",
                                                          "SSB","SSBS"),
                                           srEstimators = NULL)
```

