---
title: "Function groups diversity"
author: "JayToh"
date: '2023-05-17'
output: html_document
---

# Library:
```{r, warning = FALSE}
library(dplyr)
library(ggplot2)
library(StatisticalModels)
library(predictsFunctions)
library(janitor)
library(ggpubr)
library(openxlsx)
library(tidyr)
library(DHARMa)
library(tibble)

select <- dplyr::select

```

# Data:
1. Read in FG sorted-data
2. Remove lands whose land use and use intensity cannot be decided
```{r}
Animals <- readRDS("1.Animals_converted.rds")
Plants <- readRDS("2.Plants_converted.rds")
Fungi <- readRDS("3.Fungi_converted.rds")

```

# Renaming the funcitonal group
Change Consumers and Producers functional groups 
```{r}
Animals <- Animals %>% rename("FG_Final" = "Adult_Trophic_level_Category")
Plants <- Plants %>% rename("FG_Final" = "CSR_Final")

```


# Diversity for each FG
## Functions
```{r}
############# Function for Abundance, spp richness, Chao and Rarefied. Takes long to run!  #############
EzdiversityFG <- function(df, strategy){
  AAA <- df %>% filter(FG_Final == strategy)
  AA <- droplevels(AAA)
  A <- predictsFunctions::SiteMetrics(diversity = AA,
                                      extra.cols = c("Longitude",
                                                     "Latitude",
                                                     "Land_use",
                                                     "Intensity",
                                                     "SSB",
                                                     "SSBS",
                                                     "Years_since_fragmentation_or_conversion",
                                                     "First_conversion",
                                                     "Since_first_conversion",
                                                     "Last_conversion",
                                                     "Since_Last_conversion",
                                                     "Country",
                                                     "Biome",
                                                     "Habitat_patch_area_square_metres",
                                                     "Km_to_nearest_edge_of_habitat"))
  A$Land_use <- factor(A$Land_use, levels = c("PV", "SV", "Plantation", "Pasture", "Crop", "Urban"))
  A$Intensity <- factor(A$Intensity, levels = c("Minimal", "Light", "Intense"))
  B <- A %>% mutate(FG = strategy) %>% relocate(FG)
  B
}

```

## Animals:
Carnivore	501779			
Detritivore	162063			
Fungivore	145662			
Herbivore	536897			
Non-feeding	6381			
Omnivore	84939			
NA	201778
```{r}
### checking ###
dplyr::count(Animals, FG_Final)

### Can take a while to run, be patient! ###
Animals_Carnivore <- EzdiversityFG(Animals, "Carnivore")
Animals_Herbivore <- EzdiversityFG(Animals, "Herbivore")
Animals_Omnivore <- EzdiversityFG(Animals, "Omnivore") # Warning

Testing <- EzdiversityFG(Animals, "Omnivore")

### Final dataset here ###
Animals_FG <- rbind(Animals_Carnivore, Animals_Herbivore, Animals_Omnivore)
```


## Plant CSR
1. C, S, and R SiteMetric function for each function group
2. Drop level
3.SiteMetric
4. EzdiversityFG

```{r}
################################### Diversity for each TL. ###################################
# EzdiversityFG
Plants_C <- EzdiversityFG(Plants, "C") # Warning for rarefied
Plants_S <- EzdiversityFG(Plants, "S")
Plants_R <- EzdiversityFG(Plants, "R")

# Final dataset here
Plants_FG <- rbind(Plants_C, Plants_R, Plants_S)

```

## Fungi Saprotroph, symbiotroph, pathotroph
```{r}

Fungi_Sym <- EzdiversityFG(Fungi, "Symbiotroph")
Fungi_Sapro <- EzdiversityFG(Fungi, "Saprotroph")
Fungi_Path <- EzdiversityFG(Fungi, "Pathotroph")


# Final dataset here
Fungi_FG <- rbind(Fungi_Sym, Fungi_Sapro, Fungi_Path)

```


# Remove undecided land uses and intensities:
```{r}

AnimalsFG_clean <- Animals_FG %>% filter(!is.na(Land_use)) %>% filter(!is.na(Intensity))  
PlantsFG_clean <- Plants_FG %>% filter(!is.na(Land_use)) %>% filter(!is.na(Intensity))  
FungiFG_clean <- Fungi_FG %>% filter(!is.na(Land_use)) %>% filter(!is.na(Intensity)) 

## Check ##
dplyr::count(AnimalsFG_clean, Land_use) # Good
dplyr::count(AnimalsFG_clean, Use_intensity) # Good
dplyr::count(PlantsFG_clean, Land_use) # Good
dplyr::count(PlantsFG_clean, Use_intensity) # Good
dplyr::count(FungiFG_clean, Land_use) # Good
dplyr::count(FungiFG_clean, Use_intensity) # Good
```


## Exporting:
```{r}
saveRDS(AnimalsFG_clean, "B1.AnimalsFG_clean.rds")
saveRDS(PlantsFG_clean, "B2.PlantsFG_clean.rds")
saveRDS(FungiFG_clean, "B3.FungiFG_clean.rds")

```

